---
title: "Final Presentation"
output: html_document
---

## Final Report Presentation

By: Lydia González
December 4th, 2020

Dataset retrieved from: https://archive.ics.uci.edu/ml/datasets/Breast+Cancer+Wisconsin+%28Diagnostic%29

## Importing libraries
```{r}
library(rpart)
#install.packages("rpart.plot")
library(rpart.plot)
library(caret)
library(Metrics)
library(nnet)
library(neuralnet)
library(NeuralNetTools)
```

## Importing dataset
```{r}
bc <- read.csv("https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/wdbc.data", header = TRUE, sep = ",")
colnames(bc)[2] <- "Malignant.Benign"
bc$Malignant.Benign <- as.numeric(bc$Malignant.Benign == 'M')
```

## Building decision tree
```{r}
bc_model_1 <- rpart(formula = Malignant.Benign ~ ., data = bc, method = "class")
rpart.plot(x = bc_model_1, yesno = 2)
```

## Split into training and testing
```{r}
# Splitting 80/20
n <- nrow(bc)
n_train <- round(0.8 * n)
set.seed(123)
train_indices <- sample(1:n, n_train)

# Subsetting training data frame
bc_train <- bc[train_indices, ]

# Subsetting testing data frame
bc_test <- bc[-train_indices, ]
```

## Train model to predict class
```{r}
bc_model <- rpart(formula = Malignant.Benign ~ ., data = bc_train, method = "class")
rpart.plot(x = bc_model, yesno = 2)
```

## Generate prediction from model object
```{r}
class_prediction <- predict(bc_model, newdata = bc_test, type = "class")
confusionMatrix(class_prediction, bc_test$Malignant.Benign)
```

## Comparing models with different splitting criterion
```{r}
# Training gini-based model
bc_model_gini <- rpart(formula = Malignant.Benign ~ ., data = bc_train, method = "class", parms = list(split = "gini"))

# Training information-based model 
bc_model_info <- rpart(formula = Malignant.Benign ~ ., data = bc_train, method = "class", parms = list(split = "information"))

# Generate predictions
pred_gini <- predict(object = bc_model_gini, newdata = bc_test, type = "class")
pred_info <- predict(object = bc_model_info, newdata = bc_test, type = "class")

# Compare classification  error
ce(actual = bc_test$Malignant.Benign, predicted = pred_gini)
ce(actual = bc_test$Malignant.Benign, predicted = pred_info)
```

## Generate predicted values on test set and evaluate on AUC
```{r}
pred <- predict(object = bc_model, newdata = bc_test, type = "prob")

# Compute AUC
auc(actual = ifelse(bc_test$Malignant.Benign == "1", 1, 0), predicted = pred[, "1"])
```

## Building Neural Network
```{r}
bc1 <- read.csv("https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/wdbc.data", header = TRUE, sep = ",")
colnames(bc1)[2] <- "Malignant.Benign"
bc1$Malignant.Benign <- as.numeric(bc$Malignant.Benign == 'M')

# Create k equally sized folds
k = 10
folds <- cut(seq(nrow(bc1)), breaks = k, labels = FALSE)
accu1 <- rep(NA, k) # 1 hidden layer
accu2 <- rep(NA, k) # 2 hidden layers
accu3 <- rep(NA, k) # 3 hidden layers
```

## Create and test all models
```{r}
for (i in seq(k)){
  # Split training and testing
  test_ind <- which(folds == i, arr.ind = TRUE)
  bc1_test <- bc1[test_ind, -c(1,2)]
  bc1_train <- bc1[-test_ind, ]
  
  # Actual output
  actual <- bc1[test_ind, 2]
  
  # Create models with training data
  nn1 <- neuralnet(Malignant.Benign ~ ., bc1_train, hidden = c(30), linear.output = FALSE, 0.000001)
  nn2 <- neuralnet(Malignant.Benign ~ ., bc1_train, hidden = c(30, 30), linear.output = FALSE, 0.000001)
  nn3 <- neuralnet(Malignant.Benign ~ ., bc1_train, hidden = c(30, 30, 30), linear.output = FALSE, 0.000001)
  plotnet(nn1)
  plotnet(nn2)
  plotnet(nn3)
  
  # Run Neural Network with test data
  r1 <- compute(nn1, bc1_test)
  r2 <- compute(nn2, bc1_test)
  r3 <- compute(nn3, bc1_test)
  
  # Estimations of test results
  e1 <- round(r1$net.result)
  e2 <- round(r2$net.result)
  e3 <- round(r3$net.result)
  
  # Accuracy from estimates
  accu1[i] <- mean(e1 == actual)
  accu2[i] <- mean(e2 == actual)
  accu3[i] <- mean(e3 == actual)
  
  accu1[i]
  accu2[i]
  accu3[i]
}
```
